ext_risk_copula

### 2019-01-14 ext_risk_copula.Rmd
added results for ricker and hassell, need to fix msmith

rlist<-c(0,0.05,0.25,0.5,0.7,0.75,0.9,1.0,1.25,1.5,1.75,1.95)

# plot for local dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
pdf("./Results/ext_risk_copula/ricker_ext_risk_local_disp.pdf",heigh=6,width=10)
op<-par(mfrow=c(3,4),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    #cat("r=",r,"\n")
    s<-varying_d(numsims=10000,numsteps =10,numlocs=5,r=r,K=50,a=NA,b=NA,model="ricker",disp_everywhere=F,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend(x=-0.06,y=1.1, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# plot for local dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
pdf("./Results/ext_risk_copula/ricker_ext_risk_global_disp.pdf",heigh=6,width=10)
op<-par(mfrow=c(3,4),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    #cat("r=",r,"\n")
    s<-varying_d(numsims=10000,numsteps =10,numlocs=5,r=r,K=50,a=NA,b=NA,model="ricker",disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend(x=-0.06,y=1.1, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

![Effect of non-Normal environmental noise copula on extinction risk after 10 years (Lewton-Cohen model : $r=0$, Ricker model : $r\neq0$) with local dispersion; numlocs=5, numsteps=10, numsims=10000\label{fig_ricker_risk_local_disp}](./Results/ext_risk_copula/ricker_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 10 years (Lewton-Cohen model : $r=0$, Ricker model : $r\neq0$) with global dispersion; numlocs=5, numsteps=10, numsims=10000\label{fig_ricker__risk_global_disp}](./Results/ext_risk_copula/ricker_ext_risk_global_disp.pdf){ width=40%, height=40% }

@@

rlist<-seq(from=5,to=10,by=1)
a<-0.5
b<-1.5
K_e<-((r^(1/b))-1)/a
rc<-((b/(b-1)))^b # critical value of r from monotonic to osc steady state approach transition

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/hassell_ext_risk_local_disp.pdf",heigh=6,width=10)
op<-par(mfrow=c(2,4),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    #cat("r=",r,"\n")
    s<-varying_d(numsims=10000,numsteps =10,numlocs=5,r=r,K=K_e,a=a,b=b,model="hassell",disp_everywhere=F,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend(x=-0.06,y=0.1, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/hassell_ext_risk_global_disp.pdf",heigh=6,width=10)
op<-par(mfrow=c(2,4),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    #cat("r=",r,"\n")
    s<-varying_d(numsims=10000,numsteps =10,numlocs=5,r=r,K=K_e,a=a,b=b,model="hassell",disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend(x=-0.06,y=0.1, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

![Effect of non-Normal environmental noise copula on extinction risk after 10 years (Hassell model : a = 0.5, b = 1.5, rc=5.19) with local dispersion; numlocs=5, numsteps=10, numsims=10000\label{fig_risk_local_disp_hassell}](./Results/ext_risk_copula/hassell_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 10 years (Hassell model : a = 0.5, b = 1.5, rc=5.19) with global dispersion; numlocs=5, numsteps=10, numsims=10000\label{fig_risk_global_disp_hassell}](./Results/ext_risk_copula/hassell_ext_risk_global_disp.pdf){ width=40%, height=40% }

@@

```{r fig_msmith, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)

blist<-seq(from=1,to=2,by=0.2)
r<-5
a<-0.5
K_e<-((r-1)^(1/b))/a

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/msmith_ext_risk_local_disp.pdf",heigh=6,width=10)
op<-par(mfrow=c(3,4),mar=c(5,4,1,1) + 0.2)
for(b in blist){
    s<-varying_d(numsims=10000,numsteps =10,numlocs=5,r=r,K=K_e,a=a,b=b,model="msmith",disp_everywhere=F,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend(x=-0.06,y=0.4, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
    mtext(paste0("b = ", b))
}
par(op)
dev.off()

# plot for global dispersal in D matrix 
pdf("./Results/ext_risk_copula/msmith_ext_risk_global_disp.pdf",heigh=6,width=10)
op<-par(mfrow=c(3,4),mar=c(5,4,1,1) + 0.2)
for(b in blist){
    s<-varying_d(numsims=10000,numsteps =10,numlocs=5,r=r,K=K_e,a=a,b=b,model="msmith",disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend(x=-0.06,y=0.4, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
    mtext(paste0("b = ", b))
}
par(op)
dev.off()
```

![Effect of non-Normal environmental noise copula on extinction risk after 10 years (Maynard Smith model : a = 0.5, r = 5, bc=1.4) with local dispersion; numlocs=5, numsteps=10, numsims=10000\label{fig_risk_local_disp_msmith}](./Results/ext_risk_copula/msmith_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 10 years (Maynard Smith model : a = 0.5, r=5, bc=1.4) with global dispersion; numlocs=5, numsteps=10, numsims=10000\label{fig_risk_global_disp_msmith}](./Results/ext_risk_copula/msmith_ext_risk_global_disp.pdf){ width=40%, height=40% }

>>>>

rlist<-c(0,0.25,0.5,0.75,1.0,1.25,1.5,1.75,1.95)
numsims<-10000
numsteps<-25
numlocs<-5
a<-NA
b<-NA
K<-50
scl<-1
ext_thrs<-K/10

# plot for local dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
pdf("./Results/ext_risk_copula/ricker_ext_risk_local_disp.pdf",height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    #cat("r=",r,"\n")
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model="ricker",disp_everywhere=F,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# plot for local dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
pdf("./Results/ext_risk_copula/ricker_ext_risk_global_disp.pdf",height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    #cat("r=",r,"\n")
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model="ricker",disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Lewton-Cohen model : $r=0$, Ricker model : $r\neq0$) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_ricker_risk_local_disp}](./Results/ext_risk_copula/ricker_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Lewton-Cohen model : $r=0$, Ricker model : $r\neq0$) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_ricker__risk_global_disp}](./Results/ext_risk_copula/ricker_ext_risk_global_disp.pdf){ width=40%, height=40% }

@@

rlist<-seq(from=1.5,to=7.5,by=0.5)
numsims<-10000
numsteps<-25
numlocs<-5
a<-0.5
b<-100
K_e<-((r^(1/b))-1)/a
scl<-1
K<-K_e
ext_thrs<-K/10
rc<-((b/(b-1)))^b # critical value of r from monotonic to osc steady state approach transition

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/hassell_ext_risk_local_disp.pdf",heigh=9,width=15)
op<-par(mfrow=c(3,5),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    #cat("r=",r,"\n")
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model="hassell",disp_everywhere=F,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("topleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/hassell_ext_risk_global_disp.pdf",heigh=9,width=15)
op<-par(mfrow=c(3,5),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    #cat("r=",r,"\n")
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model="hassell",disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("topleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Hassell model : a = 0.5, b = 100, rc=2.73) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_hassell}](./Results/ext_risk_copula/hassell_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Hassell model : a = 0.5, b = 100, rc=2.73) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_hassell}](./Results/ext_risk_copula/hassell_ext_risk_global_disp.pdf){ width=40%, height=40% }

@@

```{r fig_msmith_r_vary, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)

rlist<-seq(from=1.1,to=1.9,by=0.2)
numsims<-10000
numsteps<-25
numlocs<-5
a<-0.5
b<-4
K_e<-((r-1)^(1/b))/a
K<-K_e
scl<-1
ext_thrs<-K/10

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/msmith_ext_risk_local_disp_r_variation.pdf",heigh=3,width=15)
op<-par(mfrow=c(1,5),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model="msmith",disp_everywhere=F,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# plot for global dispersal in D matrix 
pdf("./Results/ext_risk_copula/msmith_ext_risk_global_disp_r_variation.pdf",heigh=3,width=15)
op<-par(mfrow=c(1,5),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model="msmith",disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model : a = 0.5, b = 4, rc=1.5) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_msmith_r_vary}](./Results/ext_risk_copula/msmith_ext_risk_local_disp_r_variation.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model : a = 0.5, b=4, rc=1.5) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_msmith_r_vary}](./Results/ext_risk_copula/msmith_ext_risk_global_disp_r_variation.pdf){ width=40%, height=40% }
